Appendix A: Deep Reinforcement Learning

### 2022-05-31 appendices/appendix-A-definitions.Rmd
typo
More edits

In this appendix, we will go into further detail on how deep RL algorithms work.
The aim here is not to give full treatment of all deep RL methods; instead, this section is meant to serve as an abbreviated background view on model-free deep RL^[We focus on model-free methods because the agents we use in the manuscript and Appendix B are all model-free. Further, model-based algorithms generalize from the methods we discuss here except model-based agents attempt to learn or use the environment's state-transition operator, which is typically used for planning or supplementary sample generation [@suttonbarto].].
We will introduce some of the important design choices that are made for model-free deep RL algorithms and will point to specific resources that give a more complete presentation.
These sections presume some familiarity with gradient descent optimization -- see @ruder_overview_2017 for a thorough treatment.
Throughout these sections, we'll consider the environment to be an MDP which makes for a cleaner presentation and is also consistent with the referenced literature.
This treatment can be extended to the POMDP case by including observations and the emission function.

@@

\begin{table}[H]
\resizebox{\textwidth}{!}{\begin{tabular}{l l l l l}
\hline
Abbreviation & Algorithm Name                                                     & Policy     & Method \\
\hline
A2C          & Advantage Actor Critic  (Mnih et al. 2016)                         & On-policy  & Actor-critic\\
A3C          & Asynchronous A2C  (Babaeizadeh et al. 2017)                        & On-policy  & Actor-critic\\
TRPO         & Trust Region Policy Optimization  (Schulman, Levine,et al. 2017)   & On-policy  & Policy Gradient\\
PPO          & Proximal Policy Optimization  (Schulman, Wolski, et al. 2017)      & On-policy  & Actor-critic\\
DQN          & Deep Q Networks   (Mnih et al. 2015)                               & Off-policy & Value-Based\\
DDPG         & Deep Deterministic Policy Gradient   (Lillicrap et al. 2019)       & Off-policy & Actor-critic\\
TD3          & Twin Delayed DDPG  (Fujimoto, Hoof, and Meger 2018)                & Off-policy & Actor-critic\\
SAC          & Soft Actor Critic   (Haarnoja et al. 2018)                         & Off-policy & Actor-critic\\
IMPALA       & Importance Weighted Actor Learner (Espeholt et al. 2018)           & Off-policy & Actor-critic\\
\hlin
\end{tabular}}
\caption{Survey of common model-free deep RL algorithms. }
\end{table}

>>>>

In this appendix, we will go into further detail on how deep RL algorithms work.
The aim here is not to give full treatment of all deep RL methods; instead, this section is meant to serve as an abbreviated background view on model-free deep RL^[We focus on model-free methods because the agents we use in the manuscript and Appendix B are all model-free. Further, model-based algorithms generalize from the methods we discuss here except model-based agents attempt to learn or use the environment's state-transition operator, which is typically used for planning or supplementary sample generation [@suttonbarto]. The main advantage of model-based algorithms tend to be more sample efficient than model-free algorithms but can struggle to perform well when the transition dynamics are very difficult to learn.].
We will introduce some of the important design choices that are made for model-free deep RL algorithms and will point to specific resources that give a more complete presentation.
These sections presume some familiarity with gradient descent optimization -- see @ruder_overview_2017 for a thorough treatment.
Throughout these sections, we'll consider the environment to be an MDP which makes for a cleaner presentation and is also consistent with the referenced literature.
This treatment can be extended to the POMDP case by including observations and the emission function.

@@

\begin{table}[H]
\resizebox{\textwidth}{!}{\begin{tabular}{l l l l l}
\hline
Abbreviation & Algorithm Name                                                     & Policy     & Method \\
\hline
A2C          & Advantage Actor Critic  (Mnih et al. 2016)                         & On-policy  & Actor-critic\\
A3C          & Asynchronous A2C  (Babaeizadeh et al. 2017)                        & On-policy  & Actor-critic\\
TRPO         & Trust Region Policy Optimization  (Schulman, Levine,et al. 2017)   & On-policy  & Policy Gradient\\
PPO          & Proximal Policy Optimization  (Schulman, Wolski, et al. 2017)      & On-policy  & Actor-critic\\
DQN          & Deep Q Networks   (Mnih et al. 2015)                               & Off-policy & Value-Based\\
DDPG         & Deep Deterministic Policy Gradient   (Lillicrap et al. 2019)       & Off-policy & Actor-critic\\
TD3          & Twin Delayed DDPG  (Fujimoto, Hoof, and Meger 2018)                & Off-policy & Actor-critic\\
SAC          & Soft Actor Critic   (Haarnoja et al. 2018)                         & Off-policy & Actor-critic\\
IMPALA       & Importance Weighted Actor Learner (Espeholt et al. 2018)           & Off-policy & Actor-critic\\
\hline
\end{tabular}}
\caption{Survey of common model-free deep RL algorithms. }
\end{table}
